SPARQL on the Open, Decentralised Web

### 2016-07-23 dissertation/conclusions.tex
create etags

Problem~\ref{prob:queryeq} is best addressed by creating hashing
algorithms that have a reasonable chance of returning the same digest
if two queries are equivalent. As noted in Section~\ref{sec:relcache},
the approach \cite{papailiou2015graph} took to canonical labelling may
be extended to address this problem.

>>>>

Problem~\ref{prob:queryeq} is best addressed by creating hashing
algorithms that have a reasonable chance of returning the same digest
if two queries are equivalent. As noted in Section~\ref{sec:relcache},
\cite{kaseicache} can be used for this, and the approach
\cite{papailiou2015graph} took to canonical labelling may be extended
to address this problem
